---
title: "DFO species to Atlantis groups"
author: "Alberto Rovellini"
date: "5/18/2021"
output: html_document
---

Visualise how the DFO species are mapped to the Atlantis groups. Attribution of DFO species to Atlantis groups was based on the mapping already done for the RACE data, so: (1) it is only as accurate as the RACE mapping; (2) some species may fit in different Atlantis groups in GOA and BC, but that is not accounted for here. Keep an eye out for oddities.

```{r}
library(tidyverse)
library(kableExtra)
```

```{r}
select <- dplyr::select
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the DFO species list with the corresponding Atlantis group code. Read in the Atlantis groups for longer names.
```{r}
dfo_species <- read.csv("data/dfo_species_atlantis.csv")
atlantis_groups <- read.csv("data/GOA_Groups.csv", fileEncoding = "UTF-8-BOM")
```

```{r}
atlantis_groups <- atlantis_groups %>% select(Code,Name,LongName)
```

Join.
```{r}
dfo_species <- dfo_species %>% left_join(atlantis_groups, by = c("Atlantis.group"="Code"))
```

Find what species are undecided and remove them from the DFO data for now.
```{r}
paste(dfo_species %>% filter(Atlantis.group == "?") %>% select(English.common.name) %>% pull(), sep = ", ", collapse = ", ")

dfo_species <- dfo_species %>% filter(Atlantis.group != "?")
```
Many of these are generic records that could belong to multiple Atlantis groups. Some are groups that I have not yet mnade decisions about, such as hake, lingcod, and saury.

Write it all up in a table.
```{r}
species_table <- dfo_species %>% group_by(Atlantis.group) %>%
  mutate(Scientific = paste0(Scientific.name, collapse = ", "),
         Common = paste0(English.common.name, collapse = ", ")) %>%
  select(Atlantis.group, LongName:Common) %>%
  distinct()

kbl(species_table, col.names = c("Atlantis group code", "Atlantis group name", "DFO scientific name", "DFO common name")) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "40em") %>%
  column_spec(4, width = "30em")
```


